Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-05-01 overleaf/results.tex
Added comments.
evaluation section, added the big table

@@

We show circuit evaluation times in \cref{fig:graph_all_eval_time}. In terms of amenability to vectorization, we divide benchmarks into 3 categories: 1) {\it High:} these include convex hull, cryptonets max pooling, minimal points and private set intersection. These benchmarks are highly parallelizable and see 25x to 70x speedup in BMR, and 30x to 55x in GMW protocol. 2) {\it Medium:} these include biometric matching, DB Variance, histogram, inner product, k-means iteration and MNIST ReLU. These benchmarks have non-parallelizable phases e.g. the summing phase of inner product and biometric matching. Still, most computation is parallelizable and it results in speedup from 5x to 25x in BMR, and 2x to 25x in GMW protocol. 3) {\it Low:} these include the Database Join and the regular expression benchmarks (count 102, count 10, longest 102 and max distance between symbols). There is very little parallelizable computation in these programs, thus the speedup is lower. We see a speedup from 1.1x to 2x in BMR. In GMW, DB Join, Count 102 and Count 10s see speedup from 1.1x to 1.3x. However, longest 102 and max distance between symbols suffer a slowdown of 0.5x. The structure of these benchmarks is such that transformation to vectorized code increases multiplicative depth and, the negative effect of increased depth is more noticeable in a round-based protocol like GMW. We fix this via a simple heuristic where if the transformation increases circuit depth beyond some threshold (e.g. more than 10\% of the original circuit), we reject the transformation. Nevertheless, we show these graphs here for the sake of completeness and to highlight that vectorization is not always reduce run time. Note that in some settings it may still be desirable to vectorize e.g. in data constrained environments. As shown in \cref{fig:graph_comm_size}, vectorization results in reduced communication (fewer bits are transferred).

>>>>

   \begin{table*}[htbp]
       \centering
       \caption{Vectorized vs Non-Vectorized Comparison, times in seconds (in LAN setting where applicable), Communication in MiB, Numbers in 1000s, values rounded to nearest integer, benchmark names ending in {\em V} are vectorized.}
       \label{table:metrics}
       \rowcolors{5}{}{gray!10}
       \tabcolsep3pt
       \begin{tabular}{lrrrrrrrrrrrr}
           \toprule
           {} & \multicolumn{6}{c}{\textbf{GMW}} & \multicolumn{6}{c}{\textbf{BMR}} \\
            \cmidrule(r){2-7} \cmidrule(r){8-13} \\
            {\bf Benchmark} & Online & Setup & \# Gates & Circ Gen & \# Msgs & Comm. &  Online & Setup & \# Gates & Circ Gen & \# Msgs & Comm. \\
          \midrule
            Biometric Matching & 146 & 16 & 1,784 & 119 & 1,413 & 140 & 89 & 263 & 1,595 & 139 & 2,716 & 312\\
            Biometric Matching (V) & 12 & 4 & 34 & 2 & 28 & 14 & 2 & 13 & 30 & 4 & 61 & 130\\
            \midrule
            Convex Hull & 48 & 6 & 551 & 40 & 516 & 51 & 28 & 72 & 494 & 39 & 695 & 80\\
            Convex Hull (V) & 0 & 1 & 2 & 0 & 1 & 4 & 0 & 2 & 1 & 1 & 2 & 32\\
            \midrule
            Count 102 & 79 & 6 & 418 & 35 & 525 & 52 & 15 & 62 & 269 & 33 & 785 & 92\\
            Count 102 (V) & 71 & 5 & 316 & 24 & 332 & 34 & 11 & 30 & 167 & 16 & 304 & 59\\
            \midrule
            Count 10s & 79 & 6 & 419 & 35 & 525 & 52 & 14 & 62 & 270 & 33 & 785 & 92\\
            Count 10s (V) & 71 & 4 & 316 & 24 & 332 & 34 & 11 & 29 & 167 & 16 & 304 & 59\\
            \midrule
            Cryptonets (Max Pooling) & 50 & 11 & 688 & 46 & 554 & 55 & 36 & 89 & 608 & 51 & 898 & 110\\
            Cryptonets (Max Pooling) (V) & 1 & 1 & 7 & 1 & 2 & 5 & 2 & 4 & 7 & 2 & 12 & 49\\
            \midrule
            Database Join & 70 & 8 & 433 & 48 & 790 & 80 & 19 & 229 & 458 & 119 & 3,518 & 427\\
            Database Join (V) & 54 & 6 & 320 & 35 & 575 & 61 & 16 & 112 & 320 & 57 & 1,457 & 285\\
            \midrule
            Database Variance & 166 & 18 & 2,009 & 135 & 1,639 & 163 & 95 & 269 & 1,708 & 145 & 2,795 & 320\\
            Database Variance (V) & 37 & 6 & 321 & 24 & 334 & 43 & 10 & 30 & 170 & 13 & 178 & 141\\
            \midrule
            Histogram & 94 & 10 & 862 & 68 & 979 & 97 & 27 & 94 & 491 & 51 & 1,132 & 135\\
            Histogram (V) & 33 & 5 & 166 & 16 & 164 & 23 & 7 & 17 & 92 & 13 & 154 & 68\\
            \midrule
            Inner Product & 127 & 15 & 1,675 & 108 & 1,308 & 130 & 83 & 250 & 1,526 & 134 & 2,623 & 301\\
            Inner Product (V) & 16 & 5 & 158 & 12 & 165 & 25 & 6 & 18 & 83 & 7 & 86 & 127\\
            \midrule
            k-means & 108 & 12 & 1,333 & 88 & 1,090 & 108 & 63 & 185 & 1,141 & 99 & 1,958 & 225\\
            k-means (V) & 6 & 3 & 47 & 4 & 43 & 12 & 2 & 11 & 32 & 4 & 54 & 95\\
            \midrule
            Longest 102 & 93 & 7 & 650 & 52 & 713 & 71 & 26 & 93 & 475 & 49 & 1,091 & 128\\
            Longest 102 (V) & 169 & 6 & 544 & 41 & 519 & 53 & 25 & 60 & 369 & 33 & 605 & 95\\
            \midrule
            Max. Dist. b/w Symbols & 71 & 8 & 572 & 43 & 576 & 57 & 24 & 69 & 397 & 38 & 748 & 89\\
            Max. Dist. b/w Symbols (V) & 166 & 7 & 538 & 39 & 512 & 51 & 24 & 57 & 363 & 32 & 589 & 78\\
            \midrule
            Minimal Points & 35 & 5 & 458 & 31 & 369 & 37 & 24 & 46 & 401 & 26 & 347 & 40\\
            Minimal Points (V) & 0 & 1 & 1 & 0 & 1 & 3 & 0 & 1 & 1 & 0 & 1 & 16\\
            \midrule
            MNIST ReLU & 132 & 31 & 1,843 & 126 & 1,483 & 152 & 98 & 247 & 1,630 & 135 & 2,401 & 298\\
            MNIST ReLU (V) & 3 & 3 & 25 & 3 & 9 & 17 & 5 & 11 & 25 & 5 & 33 & 136\\
            \midrule
            Private Set Intersection & 95 & 9 & 558 & 59 & 1,049 & 104 & 22 & 186 & 591 & 96 & 2,639 & 302\\
            Private Set Intersection (V) & 1 & 2 & 1 & 2 & 1 & 8 & 1 & 8 & 2 & 4 & 2 & 122\\
          \bottomrule
       \end{tabular}
       \label{table:metrics}
   \end{table*}

@@

A detailed summery of the effects of vectorization on various benchmarks is presented in \cref{table:metrics}. We show circuit evaluation times in \cref{fig:graph_all_eval_time}. In terms of amenability to vectorization, we divide benchmarks into 3 categories: 1) {\it High:} these include convex hull, cryptonets max pooling, minimal points and private set intersection. These benchmarks are highly parallelizable and see 25x to 70x speedup in BMR, and 30x to 55x in GMW protocol. 2) {\it Medium:} these include biometric matching, DB Variance, histogram, inner product, k-means iteration and MNIST ReLU. These benchmarks have non-parallelizable phases e.g. the summing phase of inner product and biometric matching. Still, most computation is parallelizable and it results in speedup from 5x to 25x in BMR, and 2x to 25x in GMW protocol. 3) {\it Low:} these include the Database Join and the regular expression benchmarks (count 102, count 10, longest 102 and max distance between symbols). There is very little parallelizable computation in these programs, thus the speedup is lower. We see a speedup from 1.1x to 2x in BMR. In GMW, DB Join, Count 102 and Count 10s see speedup from 1.1x to 1.3x. However, longest 102 and max distance between symbols suffer a slowdown of 0.5x. The structure of these benchmarks is such that transformation to vectorized code increases multiplicative depth and, the negative effect of increased depth is more noticeable in a round-based protocol like GMW. We fix this via a simple heuristic where if the transformation increases circuit depth beyond some threshold (e.g. more than 10\% of the original circuit), we reject the transformation. Nevertheless, we show these graphs here for the sake of completeness and to highlight that vectorization is not always reduce run time. Note that in some settings it may still be desirable to vectorize e.g. in data constrained environments. As shown in \cref{fig:graph_comm_size}, vectorization results in reduced communication (fewer bits are transferred).
